### 2014-03-14 src/analysis.Rnw
update

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:locsel}
\end{figure*}

\begin{figure*}[t]
<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
\label{fig:wlocsel}
\end{figure*}

@@

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of one element selection, All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

@@

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\end{figure*}

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
#4
@

>>>>

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
<<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:locsel}
\end{figure*}

\begin{figure*}[t]
<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
@
\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
\label{fig:wlocsel}
\end{figure*}

@@

\begin{figure*}[t]
<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
@
\caption{The effect of one element selection, All are above 0.98 $R^2$.}
\label{fig:onesel}
\end{figure*}

@@

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\end{figure*}

% \begin{figure*}[t]
% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
% \end{figure*}
%

% \begin{figure*}[t]
% <<op.all.3,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% dfd <- subset(df, !(strategy %in% c('op','opsel')) )
% ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
% @
% \label{fig:fullimgshape}
% \end{figure*}
<<opsel>>=
#4
@

### 2014-03-14 src/related.Rnw
update

Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
strategies on top of operator based mutant selection and find that sampling strategies
based on program components (based on methods) performed best.

>>>>

Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
was sufficient for a very high correlation (99\%) with the full mutation score, while sampling even
fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
strategies on top of operator based mutant selection and find that sampling strategies
based on program components (based on methods) performed best.
